Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-11-24 ATACCC.tex
Improve plots + typos
add todo

Let the observed log viral load for individual $i$ at time $t$ be $y_{i,t}$, with $y_{i,t}=0$ if the test is negative.
Then, its likelihood is:
\begin{align}
p(y_{i,t} \mid \cdot) &= \begin{cases}
    \rho f_N(y_{i,t} \mid x_0, \sigma_0^2) + (1 - \rho) f_N(y_{i,t} \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} > v_\text{lod}$}\\
    \rho F_N(v_\text{lod} \mid x_0, \sigma_0^2) + (1 - \rho) F_N(\vlod \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} = v_\text{lod}$} \label{ATACCC:eq:hakki-likelihood}
\end{cases}
\end{align}
where $f_N(y \mid \mu, \sigma^2)$ and $F_N(y \mid \mu, \sigma^2)$ are the pdf and cdf at $y$ of a Normal distribution with mean $\mu$ and variance $\sigma^2$ respectively.
The first term on each line is the likelihood contribution from test failures, either a false positive (top line) of false negative (bottom line).
The second term on the first line is the likelihood of the observed log viral load from non-failed test results.
The second term on the bottom line is the likelihood of the negative (censored) tests from non-failed test results.

@@

>>>>

Let the observed log viral load for individual $i$ at time $t$ be $y_{i,t}$, with negative tests signified by $y_{i,t}=v_\text{lod}$.
Then, its likelihood is:
\begin{align}
p(y_{i,t} \mid \cdot) &= \begin{cases}
    \rho f_N(y_{i,t} \mid x_0, \sigma_0^2) + (1 - \rho) f_N(y_{i,t} \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} > v_\text{lod}$}\\
    \rho F_N(v_\text{lod} \mid x_0, \sigma_0^2) + (1 - \rho) F_N(\vlod \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} = v_\text{lod}$} \label{ATACCC:eq:hakki-likelihood}
\end{cases}
\end{align}
where $f_N(y \mid \mu, \sigma^2)$ and $F_N(y \mid \mu, \sigma^2)$ are the pdf and cdf at $y$ of a Normal distribution with mean $\mu$ and variance $\sigma^2$ respectively.
The first term on each line is the likelihood contribution from test failures, either a false positive (top line) of false negative (bottom line).
The second term on the first line is the likelihood of the observed log viral load from non-failed test results.
The second term on the bottom line is the likelihood of the negative (censored) tests from non-failed test results.

@@

\todo[inline]{Probably important to show estimated test sensitivity here to refer to later}
